---
title: "Assignment 2 part 2"
author: "Smitesh Patil"
date: "2023-03-21"
output: pdf_document
---

```{r include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
#ignore warnings
options(warn=-1)
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```
\normalsize Q2.4 Provide a brief interpretation of the meaningful contextual topics uncovered by the
community detection algorithm for each word pair. If the uncovered topic appears to have no
apparent relevance to either of the words in your word pair you may declare it as ‘nonrelevant’. You can present these interpretations in the same table where the communities are
listed, if there is room. If you present the interpretations in a separate table, the rows must be
numbered to refer to the community numbers in the first table.

```{r}
table1 <- as_tibble(read.csv("table1.csv"))

table2 <- as_tibble(read.csv("table2.csv"))

table3 <- as_tibble(read.csv("table3.csv"))
```

```{r}

table1 %>% 
  arrange(desc(Size)) %>%
  filter(Size > 3)
  select


table2 %>% 
  arrange(desc(Size)) %>%
  filter(Size > 3)


table3 %>% 
  arrange(desc(Size)) %>%
  filter(Size > 3)

```



