---
title: "Assingment 1"
output:
  pdf_document: default
  html_document: default
date: '2023-01-25'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Basic measures

```{r}

library(igraph)
dib_graph<-read.graph("dib2.graphml",format="graphml")

```

1.1 Give the number of nodes and edges

```{r}
cat("num vertices:", vcount(dib_graph), "\n")

cat("num edges :", ecount(dib_graph), "\n")
```
1.2 Is the network strongly or weakly connected. If neither, what is the distribution of
component sizes.


```{r}
strong_component = as.data.frame(table(factor(components(dib_graph, mode="strong")$csize)))
names(strong_component)[1] = "Component Size"
strong_component
```

The table above shows strongly connected components in the directed network. There is one component with 5479, 6 and 5 nodes and a distribution of component with sizes varying from 1 to 4.

```{r}
weak_component = as.data.frame(table(factor(components(dib_graph, mode="weak")$csize)))
names(weak_component)[1] = "Component Size"
weak_component
```

The table above shows weakly connected components in the directed network. There is one component with 8872 and 4 nodes with 30 weakly connected components of size 2 and 11 components with size 3.

1.3 What is the diameter of the network ?

```{r}
cat("The diamter of the network is : ", diameter(dib_graph, directed = T, unconnected = TRUE, weights=NA), "\n")
```
1.4 What is the average path length of the network ?

```{r}
cat("The average path length of the network :", mean_distance(dib_graph, directed = T), "\n")
```
1.5 What is the clustering coefficient of the network ?

```{r}
cat("clustering coeff of the graph is :", transitivity(dib_graph, type="localaverage"), "\n")
```
1.6 What is the in- and out-degree distribution ?

```{r}
deg<-degree(dib_graph, mode = "in")

hist(deg, 
     breaks=(min(deg)-1):(max(deg))+0.5,
     freq=FALSE, 
     xlab = "in-degree", 
     ylab = "proportion", 
     main = "Histogram of In-Degree Distribution",
     border="#80b1d3", 
     col="#8dd3c7", 
     xlim=c(0,max(deg)),
     ylim=c(0,0.06))
```

```{r}
deg<-degree(dib_graph, mode = "out")

hist(deg, 
     breaks=(min(deg)-1):(max(deg))+0.5,
     freq=FALSE, 
     xlab = "in-degree", 
     ylab = "proportion", 
     main = "Histogram of Out-Degree Distribution",
     border="#80b1d3", 
     col="#8dd3c7", 
     xlim=c(0,max(deg)),
     ylim=c(0,0.06))
```