---
title: "Training Intervention Analysis"
author: "your name, id=your student id"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default
---
 **Before you start: if you are a Mac user, you will need to install Xquartz from https://www.xquartz.org so you can use the 'tolerance' package.**  You can delete this line from your final report.  

```{r include=FALSE}
library(infer)
library(tidyverse)
library(tolerance)
```

## Context: Celtic Study

A sample of 18 full-time youth soccer players from a Youth Academy performed high intensity aerobic interval training over a 10-week in-season period in addition to usual regime of soccer training and matches. 

**The aim** of this study to find if this extra training improves V_IFT, the maximum velocity (km/hr) achieved in an intermittent fitness test (`VIFT_Pre` vs `VIFT_Post`)?

This is a **paired design:** each player's V_IFT measured before and after the training intervention (i.e. start and after 10 weeks)

A scaffold for the analysis with the response variable VO2 max is provided below. You need to rerun the analysis using the V_IFT variables (i.e. `VIFT_Pre` vs `VIFT_Post`) to answer the question of interest: is there, on average, an improvement in V_IFT?   To assess the evidence, you will provide confidence intervals, and other statistical inference,  for the mean improvement of players in the population (eg of future youth soccer players under the same training intervention).


To answer the question of interest, provide a detailed response for all of the tasks asked below using the V_IFT variables (i.e. `VIFT_Pre` vs `VIFT_Post`).


Task: State the appropriate null and alternative hypotheses for the V_IFT study.


Task: Define a Type I and Type II error and discuss the implication of making these
errors in this study.



## Read in the training intervention data

Read in the data and have a look at the variable names and structure of the data.

```{r}
train.df <- read.csv("Training_intervention_data.csv")
glimpse(train.df)
```

## Focus on the V_IFT response variables

## Summary Statistics

```{r}
train.df %>% select(VIFT_Pre,VIFT_Post) %>% summary()
```
Task: Interpret!

Answer: From the above measures it can be interpreted that extra training does in fact help with improving athlete's maximum velocity. The minimum and maximum value of VIFT is increased  post training. also previous 50% of athletes lied between the range of 23.65 to 29.20 after the training it increased to 25.43 to 31.50.

## Mean and Standard Deviation

```{r}
train.df %>% select(VIFT_Pre,VIFT_Post) %>%
            summarize(Pre_Mean=mean(VIFT_Pre), Pre_SD= sd(VIFT_Pre),
                      Post_Mean=mean(VIFT_Post), Post_SD= sd(VIFT_Post))
```

Task: Interpret!

Answer : It can be observed that there is a significant improvement in the maximum velocity achieved post extra training before  it was around 26.01 +/- 3.17 after training it jumped to around 28.07 +/- 3.72

## Scatterplot of Pre and Post with line of equality

```{r}

train.df %>% ggplot(aes(x = VIFT_Pre, y = VIFT_Post)) +
        geom_point() + 
  ggtitle("Scatterplot of Pre and Post VIFT") +
  ylab("Post Vift (ml/kg min)") +
  xlab("Pre Vift (ml/kg min)") +
  geom_abline(slope=1, intercept=0)
  
```

Task: Interpret!

Answer: In the above scatter plot it is observed that 2 players out of 18 have actually performed worse in VIFT after the extra training they received. first player had a Pre VIFT of 23.8 which declined too 23.3 after training and second player had a vift of 25.3 which declined to 24.3

## Calculate the Improvement in V_IFT

Calculate a new variable, "improvement", and have a look at the data frame to see that it has been created.  High values of VO2 max are good so Post-Pre is a better measure than Pre-Post to capture this - what about V_IFT?

```{r}

train.df <- train.df %>% mutate(Improvement = VIFT_Post-VIFT_Pre) %>%
              glimpse()

```


## Mean and Standard Deviation of Improvement in V_IFT

```{r}

train.df %>% select(Improvement) %>%
            summarize(Imp_Mean=mean(Improvement), Imp_SD= sd(Improvement))

```

Task: Interpret!

Answer: So on average a player improves his VIFT by 2.06 by pursuing the extra training, but the standard deviation is  quite high it is almost close to the value of mean. Hence, the data is more spread out.

## Boxplot of Improvement in V_IFT

```{r}


train.df %>% ggplot(aes(x = "", y = Improvement)) +
        geom_boxplot() + 
  ggtitle("Boxplot of Improvement in VIFT") +
  ylab("Improvement in VIFT (ml/kg min)") +
  xlab("") +
  coord_flip()

train.df %>% select(Improvement) %>% summ
```

Task: Interpret!

Answer : There are outliers after the lower tail that represents the two players who should a decrease in VIFT values after the extra training. Inter-quartile ranges from 0.650 to 3.200 i.e 50% of players showed improvement between that range.


## 95% Confidence Interval Using the t.test function

```{r}

train.df %>% select(Improvement) %>% t.test()

```

Task: Based on the output given answer the following questions:

* What is the mean improvement in V_IFT the population of interest? Interpret the relevant 95% Confidence Interval carefully.

* Use the relevant interval estimate and p-value to decide whether there is sufficient evidence in the sample provided to claim that there is any improvement on average in V_IFT in the population of interest.

* What are the assumptions underlying the one sample t-test presented?

* Explain why or why not the assumptions seem justified based on the output provided.

## 95% Bootstrap CI for the mean

```{r}

boot <- train.df %>%
  specify(response = Improvement) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "mean")

percentile_ci <- get_ci(boot)
round(percentile_ci,2)

```

Task: Interpret!

```{r}
boot %>% visualize()+
  shade_confidence_interval(endpoints = percentile_ci) +
                   xlab("Bootstrap Mean") + ylab("Frequency")

```

Task: Interpret!

## 95% Bootstrap CI for the median improvement

```{r}

boot.median <- train.df %>%
  specify(response = Improvement) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "median")

percentile_ci_median <- get_ci(boot.median)
round(percentile_ci_median,2)

```

Task: Interpret!

```{r}
boot.median %>% visualize()+
  shade_confidence_interval(endpoints = percentile_ci_median) +
                   xlab("Bootstrap Median") + ylab("Frequency")

```

Task: Interpret!



## 95% Tolerance Interval (Bonus Question)

Calculate a 95% tolerance interval covering 95% of V_IFT improvement values 

```{r}

normtol.int(train.df$Improvement, alpha = 0.05, P = 0.95)

```

Task: Interpret!


## Overall Conclusion 
Task: state your overall conclusion. 


 



